Governing through patronage: the bargain for education in decentralized Brazil

### 2020-11-16 paper/paper.tex
create new descriptives by year for rais

Table \ref{tbl:descriptive_teacher} provides some additional descriptive statistics regarding teachers. The teacher labor force is highly educated and primarily composed of women, and schools in Brazil are relatively small, with an average of 4 teachers per school. As for school principals, while

>>>>

Table \ref{tbl:descriptive_teacher} provides some additional descriptive statistics. The teacher labor force is highly educated, with over 70 percent of teachers holding a higher education degree. The majority of teachers are women, and schools have a limited amount of teachers, with an average of 4 per school.
